Reanalysis Step 2: Multiple Imputation (Clean Version)

### 2025-08-29 reanalysis-2-multiple_imputation_clean.qmd
rollback 2l; failing

# Continuous variables - use 2l.pmm for clustering
for (var in vars_impute_continuous) {
  if (var %in% names(methods)) {
    methods[var] <- "2l.pmm"
  }
}

@@

# Mark cluster variable for 2-level imputation
# -2 indicates this is the cluster ID
pred_matrix[cluster_var, ] <- 0  # Don't predict the cluster ID

# For 2l.pmm variables, ensure cluster is marked
vars_2l <- names(methods)[methods == "2l.pmm"]
for (var in vars_2l) {
  pred_matrix[var, cluster_var] <- -2
}

>>>>

# Continuous variables - use standard PMM (no multilevel)
for (var in vars_impute_continuous) {
  if (var %in% names(methods)) {
    methods[var] <- "pmm"
  }
}

@@

# No multilevel imputation: ensure cluster ID is not used as predictor
pred_matrix[, cluster_var] <- 0
pred_matrix[cluster_var, ] <- 0
